A longitudinal analysis of the social information in infants' naturalistic

### 2022-07-19 paper/manuscript/appendix.Rmd
reorganization of manuscript folder & final updated figures

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)
library(papaja)
library(lme4)
library(xtable)
library(lmerTest)
theme_set(theme_few())
knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

ggsave('appendix_figs/handdensity.pdf', width = 7, height = 3)
```

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

ggpubr::ggarrange(p1, p2)
ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3.4)

@@

```{r}
face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Face detections') + 
  theme(legend.position = 'none')

hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

@@

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.env="figure", fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
ggsave('appendix_figs/rocs.pdf', width = 7, height = 3)
```

@@

f_faces = ggplot(data=roc_data, aes(x=detection_threshold, y=f_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Face detections') +
  theme(legend.position = 'none')

f_hands = ggplot(data=roc_data, aes(x=detection_threshold, y=f_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

@@

ggpubr::ggarrange(f_hands, f_faces, nrow=1)
ggsave('appendix_figs/f_scores_by_thres.pdf', width = 7, height = 3)
ggsave('appendix_figs/f_scores_by_thres.png', device = "png", width = 7, height = 3)

@@

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

ggpubr::ggarrange(p1, p2, nrow=1)
ggsave('appendix_figs/fscore_by_age_child.pdf', width = 7, height = 5)
```

@@

```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=12) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=12) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

ggpubr::ggarrange(p1, p2, nrow=1)
ggsave('appendix_figs/fscore_by_location.pdf', width = 7, height = 3)
```

@@

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.5) +
  # geom_point(alpha=.2, data = goldset) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=10)) +
  theme(legend.position="bottom")

ggsave('appendix_figs/humans_vs_op.pdf', width = 7, height = 5)

@@

ggsave('appendix_figs/activities_by_location.pdf', width = 8, height = 4)

@@

ggsave('appendix_figs/activities_by_single_location.pdf', width = 7, height = 4)

@@

ggsave('appendix_figs/prob_activity_by_single_location.pdf', width = 8, height = 4)
```

@@

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
  ggthemes::scale_color_solarized(name = "")  +
  ggthemes::scale_fill_solarized(name = "") +
  theme(legend.position = c(0.8, 0.1))

ggsave('appendix_figs/face_hand_density.pdf', width = 7, height = 7)
```

@@

```{r}
ggplot(face_hand_by_age_milestones,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=walking)) +
  geom_point(alpha=.3) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(region ~ child_name) +
  theme_few(base_size=10) +
  viridis::scale_color_viridis(name = "", option="C", discrete=TRUE, begin=0, end=.4) +
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="bottom")

ggsave('appendix_figs/face_hand_by_motor.pdf', width=7, height=5)
```

>>>>

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)
library(papaja)
library(lme4)
library(xtable)
library(lmerTest)
library(viridis)
theme_set(theme_few())
knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

ggsave('figs_publication_final/figurea2_handdensity.pdf', width = 7.2, height = 3)
```

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% 
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=10) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

ggpubr::ggarrange(p1, p2)
ggsave('figs_publication_final/figurea3_op_falsepositives.pdf', width = 7.2, height = 3.4)

@@

```{r}
face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
  theme_few(base_size=10) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Face detections') + 
  theme(legend.position = 'none')

hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
  geom_point() +
  theme_few(base_size=10) +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

@@

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.env="figure", fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
ggsave('figs_publication_final/figurea4_rocs.pdf', width = 7.2, height = 3)
```

@@

f_faces = ggplot(data=roc_data, aes(x=detection_threshold, y=f_faces, color=detection_threshold)) +
  geom_point() +
  theme_few(base_size=10) +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Face detections') +
  theme(legend.position = 'none')

f_hands = ggplot(data=roc_data, aes(x=detection_threshold, y=f_hands, color=detection_threshold)) +
  theme_few(base_size=10) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

@@

ggpubr::ggarrange(f_hands, f_faces, nrow=1)
ggsave('figs_publication_final/figurea4b_fscore_by_thres.pdf', width = 7.2, height = 3)
ggsave('figs_publication_final/f_scores_by_thres.png', device = "png", width = 7, height = 3)

@@

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=10) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.6) +
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=10) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.6) +
  theme(legend.position= 'none')

ggpubr::ggarrange(p1, p2, nrow=1)
ggsave('figs_publication_final/figurea5_fscore_by_age_child.pdf', width = 7.2, height = 4)
```

@@

```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=10) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  # scale_color_viridis(option='mako', discrete=TRUE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=10) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  # scale_color_viridis(option='mako', discrete=TRUE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

ggpubr::ggarrange(p1, p2, nrow=1)
ggsave('figs_publication_final/figurea6_fscore_by_location.pdf', width = 7.2, height = 3)
```

@@

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  # geom_point(alpha=.2, data = goldset) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) +
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE, lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE, lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=10) +
  scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=10)) +
  theme(legend.position="bottom")

ggsave('figs_publication_final/figurea7_humans_vs_op.pdf', width = 7.2, height = 4)

@@

ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)

@@

ggsave('figs_publication_final/figurea8b_activities_by_single_location.pdf', width = 7.2, height = 4)

@@

ggsave('figs_publication_final/figurea8b_prob_activity_by_single_location.pdf', width = 7.2, height = 4)
```

@@

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
      scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
      scale_fill_manual(values = c("#1266a2","#CB4B16"), name = "") +
  theme(legend.position = c(0.8, 0.1))

ggsave('figs_publication_final/figurea9_face_hand_density.pdf', width = 7, height = 7)
```

@@

```{r}
ggplot(face_hand_by_age_milestones,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=walking)) +
  geom_point(alpha=.3) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(region ~ child_name) +
  theme_few(base_size=10) +
  viridis::scale_color_viridis(name = "", option="C", discrete=TRUE, begin=0, end=.4) +
  theme(legend.text=element_text(size=10)) +
  guides(size = 'none') +
  theme(legend.position="bottom")

ggsave('figs_publication_final/figurea10_face_hand_by_motor.pdf', width=7.2, height=5)
```

### 2022-07-19 paper/manuscript/manuscript_april2022_apa_blinded.Rmd
reorganization of manuscript folder & final updated figures

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)
library(here)
library(papaja)
theme_set(theme_few())
```

@@

```{r}
first_panel <- ggplot(all_detections, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="bottom") +
  ggtitle('A.')

second_panel <- ggplot(centered, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total),linetype = 'dashed', show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="bottom")  +
  ggtitle('B.')

third_panel <- ggplot(detailed, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  scale_color_manual(values = c("#751098","#142c83"), name = "") +
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="bottom") +
  ggtitle('C.')

@@

cowplot::plot_grid(first_panel, second_panel, third_panel, labels=NULL, nrow=3, label_fontface = "bold", align = "v", axis = "b")
ggsave('figs_pdfs/test.pdf', width = 7, height = 9)
```

@@

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face and hands detection within frames where hands (left) or faces (right) were detected." }
ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion joint hand/face detection') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  ylim(0,1) +
  facet_grid(~region) +
  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=10))

ggsave('figs_pdfs/face_hand_contingency.pdf', width=7, height=3, units='in')
```

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=10) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "log(Detections)") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
  theme(legend.text=element_text(size=8))

ggsave('figs_pdfs/dets_by_location.pdf', width=7, height=5, units='in')
```

@@

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  theme_few(base_size=12) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log area (average proportion of frame)') +
  xlab('Age (in months)') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)

ggsave('figs_pdfs/size_by_age.pdf', width=7, height=3, units='in')
```

@@

```{r}
eye_dist_plot <- ggplot(eye_dist, 
       aes(x=age_day_bin, y=eye_distance, 
           col=child_id)) +
  geom_point(alpha=.15, aes(size=num_faces), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_faces), show.legend = TRUE) + 
  ylab('Avg. distance between eyes') + 
  xlab('Age (in months)') +
  theme_few(base_size=12) +
  facet_grid(~variable) +
  scale_color_brewer(palette="Dark2", name='Child') +
  guides(size = FALSE) +
  ggtitle('A.') +
  theme(legend.text=element_text(size=12))  +
  theme(legend.position="none")
```

@@

```{r}
CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
  theme_few(base_size=12) +
  geom_point(alpha=.15) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  ggtitle('B.') +
  scale_color_brewer(palette='Dark2', name='Child') + 
  ylab('Coefficient of variation') +
  xlab('Age (in months)') +
  guides(size = FALSE) 
```

@@

cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
ggsave('figs_pdfs/detailed_changes.pdf',units='in',width=7, height=3)
```
In a final set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
In particular, we explored this keypoint dataset with the idea that greater mobility allows older children to be further from their caregivers on average. 
Thus, younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
The same dynamic would be predicted hold for hands as well, as it would be driven by overall differences in distance.

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)
library(here)
library(papaja)
library(viridis)
theme_set(theme_few())
```

@@

```{r}
first_panel <- ggplot(all_detections, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
  theme(legend.text=element_text(size=10)) +
  guides(size = "none") +
  theme(legend.position="none", aspect.ratio=.75) 
  # ggtitle('A.')

  # scale_color_manual(values = c("#1266a2","#1b91e6", "#CB4B16","#eb7443"), name = "") +

second_panel <- ggplot(centered, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total),linetype = 'dashed', show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  # scale_color_viridis(option = "turbo", discrete=TRUE, begin=0.05, end=.85, name="") +
  # scale_color_manual(values = c("#92c5de","#ef8a62"), name = "") +
      scale_color_manual(values = c("#1b91e6","#eb7443"), name = "") +
  theme(legend.text=element_text(size=10)) +
  guides(size = "none") +
  theme(legend.position="none", aspect.ratio=.75)  
  # ggtitle('B.')

third_panel <- ggplot(detailed, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.1) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(cols = vars(child_name)) + 
  theme_few(base_size=10) +
  # scale_color_viridis(option = "viridis", discrete=TRUE, begin=0.3, end=.8, name="") + 
  # scale_color_manual(values = c("#751098","#142c83"), name = "") +
  scale_color_manual(values = c("#a21266","#142c83"), name = "") +
  theme(legend.text=element_text(size=10)) +
  guides(size = "none") +
  theme(legend.position="none", aspect.ratio=.75) 
  # ggtitle('C.')

@@

cowplot::plot_grid(first_panel, second_panel, third_panel, labels='auto', nrow=3, label_fontface = "bold", align = "hv", axis = "b")
ggsave(filename='figs_publication_final/figure2_updated.pdf', width = 7.2, height=8, dpi=300)
```

@@

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face and hands detection within frames where hands (left) or faces (right) were detected." }
ggplot(face_hand_contingency %>% filter(num_frames_total>20000), 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion joint hand/face detection') + 
  xlab('Age (Months)') +
  theme_few(base_size=10) +
  ylim(0,1) +
  facet_grid(~region) +
  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
  # scale_color_brewer(palette="Dark2", name = "Child") +
  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
  guides(size = "none") +
  theme(legend.text=element_text(size=6), legend.position = "none")

ggsave('figs_publication_final/figure3_face_hand_contingency.pdf', width=3.5, height=2.625, units='in')
```

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.05, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.8), size=.3) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=10) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  + 
  scale_size_continuous(name = "") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  # scale_color_manual(values = c("#1a2591", "#7fb8f1", "#b9221f","#ea5e5c"), name = "") +
  scale_color_manual(values = c("#1266a2","#1b91e6", "#CB4B16","#eb7443"), name = "") +
  theme(legend.text=element_text(size=8)) +
  guides(size = "none")

ggsave('figs_publication_final/figure4_dets_by_location.pdf', width=7.2, height=5, units='in')
```

@@

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  theme_few(base_size=10) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  theme(text=element_text(family="Helvetica"))  +
  geom_smooth(method='lm', size=1) + 
  ylab('Log area (average proportion of frame)') +
  xlab('Age (in months)') +
  # scale_color_brewer(palette="Dark2", name = "Child") +
  theme(legend.position='none') +
  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
  guides(size = "none")

ggsave('figs_publication_final/figure5_size_by_age.pdf', width=3.5, height=2.625, units='in')
```

@@

```{r}
eye_dist_plot <- ggplot(eye_dist, 
       aes(x=age_day_bin, y=eye_distance, 
           col=child_id)) +
  geom_point(alpha=.15, aes(size=num_faces), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_faces), show.legend = TRUE) + 
  ylab('Avg. distance between eyes') + 
  xlab('Age (in months)') +
  theme_few(base_size=10) +
  facet_grid(~variable) +
  # scale_color_brewer(palette="Dark2", name='Child') +
    scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
  guides(size = 'none') +
  # ggtitle('A.') +
  theme(legend.text=element_text(size=12))  +
  theme(legend.position="none")
```

@@

```{r}
CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
  theme_few(base_size=10) +
  geom_point(alpha=.15) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  # ggtitle('B.') +
  # scale_color_brewer(palette='Dark2', name='Child') +
  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
  theme(legend.position='none') +
    ylab('Coefficient of variation') +
  xlab('Age (in months)') +
  guides(size = 'none') 
```

@@

cowplot::plot_grid(eye_dist_plot, CV_faces_plot, labels='AUTO', rel_widths=c(1,2))
ggsave('figs_publication_final/figure6_detailed_changes.pdf',units='in',width=7, height=3)
```
In a final set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
In particular, we explored this keypoint dataset with the idea that greater mobility allows older children to be further from their caregivers on average. 
Thus, younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
The same dynamic would be predicted hold for hands as well, as it would be driven by overall differences in distance.
